---
title: "What the Package Does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 5,
  fig.height = 5
)
```

```{r setup}
library(wats0079MATH4753)
```

# Introduction

This package stores the major functions created in several of the MATH 4753 laboratories throughout the semester. In addition, it includes a data set.

The following functions are briefly described, and an example of each function being used is shown as well.

## First Function: myboot2

This function creates bootstrap confidence intervals for sampling. It returns a graphical representation of the boostrap interval.

```{r}
myboot2(x=fire$DISTANCE)
```

## Second Function: mycltu

This function verifies a uniform distribution based on the theory behind the Central Limit Theorem. It returns a histogram of the density curves for the population and sample.

```{r}
mycltu(n=10, iter=100000, a=0, b=10)
```

## Third Function: mybin

This function performs a binomial simulation based on the number of iterations, the sample size, and the probability of a success on a given trial. It returns a list of the relative frequencies of successes for each trial (sample) and a graph that models the simulation.

```{r}
mybin(iter=100,n=10,p=0.7)
```

## Fourth Function: mymaxlik

This function calculates the maximum log likelihood for a given sample using a specific log function. It returns a summary of the parameter of interest and a graph of where the sample values and parameter of interest intersect.

```{r}
y = c(2,4,4,6,4,4,2)
logbin=function(x,param) log(dbinom(x,prob=param,size=20))
mymaxlik(x=y,param=seq(0,1,length=1000),lfun=logbin,xlab=expression(pi),main="Binomial",cex.main=2)
```

## Data Set: fire

Below is the fire data set, which contains information on the distance (in miles) from 15 fire stations and the cost of damage (in thousands of dollars).

```{r}
data("fire")
knitr::kable(head(fire))
```
